2. Simulated Data

### 2021-08-06 analysis/reports/rmd/02_dataProcessing.Rmd
generate session info meta data

library(data.table)
library(magrittr)
library(stringr)
library(glue)
library(DescTools) # gini coefficient
library(kableExtra)
library(downloadthis)
```

@@

rm(list = c("files", "temp", "full"))
```

```{r readData, eval = FALSE}
# read replication data
DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
               stringsAsFactors = FALSE) %>%
  data.table()

# subset complete cases
DT <- DT[participant._index_in_pages == 77 & !is.na(dPGG.1.player.contribution)]
```

@@

# save data
fileName <- "replication2021"
save(replicationFirstRound, file = paste0("../../../data/processed/rda/", fileName, "_R1", ".rda"))
write.csv(replicationFirstRound, file = paste0("../../../data/processed/csv/", fileName, "_R1", ".csv"))

@@

```{r}
replication[,
            .(contribution = mean(contribution),
              endowment = mean(endowment),
              share = mean(contribution/endowment),
              share2 = mean(share)),
            by = c("round")]
```

>>>>

library(data.table)
library(magrittr)
library(lubridate)
library(stringr)
library(glue)
library(DescTools) # gini coefficient
library(kableExtra)
library(downloadthis)
```

@@

rm(list = c("files", "temp"))
```

```{r readData, eval = FALSE}
# read replication data
# DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
#                stringsAsFactors = FALSE) %>%
#   data.table()

# subset complete cases
# DT <- DT[participant._index_in_pages == 77 & !is.na(dPGG.1.player.contribution)]
```

## Meta data

```{r meta}
meta_long <- full[participant.time_started != "" & 
                    participant.label != "",
                  .(session.code,
                    participant.time_started,
                    dPGG.1.player.contribution)]

meta_long[,
          `:=`(date = participant.time_started %>% ymd_hms() %>% date(),
               hour = participant.time_started %>% ymd_hms() %>% hour())]

meta <- meta_long[,
                  .(date = date %>% unique(),
                    time = hour %>% unique() %>% paste("00", sep = ":"),
                    showups = participant.time_started %>% length(),
                    dropouts = dPGG.1.player.contribution %>% is.na() %>% sum(na.rm = FALSE)),
                  by = session.code]

meta[,
     `:=`(participants = showups - dropouts,
          observations = (showups - dropouts)/4)]

# save data
fileName <- "replication2021"
save(meta, file = paste0("../../../data/processed/rda/", fileName, "_meta", ".rda"))
write.csv(meta, file = paste0("../../../data/processed/csv/", fileName, "_meta", ".csv"))

rm(list = c("full", "meta_long"))
```

@@

# save data
save(replicationFirstRound, file = paste0("../../../data/processed/rda/", fileName, "_R1", ".rda"))
write.csv(replicationFirstRound, file = paste0("../../../data/processed/csv/", fileName, "_R1", ".csv"))

@@
